---
title: "R Class and Package for Generating Crosswords"
subtitle: "R Meetup Hamburg"
author: "Peter Meissner"
date: "01 July 2017"
output: 
  beamer_presentation: 
    fonttheme: professionalfonts
    toc: yes
  ioslides_presentation: 
    logo: ~/Dropbox/RPackages/crossword/logo/Logo_128.png
    transition: faster
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, width.cutoff=120)
```


## Usage

```{r}
library(crossword)

cw <- 
  Crossword$new(rows = 4, columns = 4)
```

## Usage

```{r}
cw$add_words(
  c("back", "nasa", "kick", "nuk", "ic", "sic")
)
```


## Usage 

```{r}
cw
```



## Data

```{r}
cw$letters
```

## Data

```{r}
cw$words
```


## Technicalities

- OOP:
    * not a fan of OOP ... but!
    * multiple pieces of data that only make sense together
    * easier to iterate on data and functions at the same time
    * state is important - adding words depends on the grid state
    * R6 (easy to use classes for traditional OOP)

## Technicalities

- data fields: 
    * `rows` (integer)
    * `columns` (integer)
    * `letters` (matrix)
    * `words` (data.frame)
    * [`restrictions_right`, `restrictions_down` (data.frame)]
    
## Technicalities

- methods: 
    * `initialize()` (row, columns)
    * `add_words()` (words, clues)
    * `density()` 
    * [`put_word_on_grid()`, `add_words()`, `update_grid_data()`, `print()`]


## Algorithm?

- quite dumb 
- loop over words
- data on cells: 
    * space (right/down)
    * letters already placed
- adding word
    * which cells have enough space
    * which cell's regex match the word
- placing based on weighting of cells 
    * balance right and down
    * try to put in the center of grid
    * try to cross as many letters on grid as possible




## End

- Peter Meissner
    * `twitter  <- "marvin_dpr"`
    * `homepage <- "pmeissner.com"`
    *  `Github   <- "petermeissner"`
    
    

- crossword
    * `status <- "work in progress"` 
    * `url <- "https://github.com/petermeissner/crossword"`



